







\section{Background}
\label{sec:background}
\subsection{Access Control Architectures}
Access control systems are regulated by access control policies that specify the different actions that subjects are able to undertake on system resources. 
An access control policy is enforced by one or multiple Policy Enforcement Points (PEP) at the application level. A PEP receives a subject access request and 
sends it to a Policy decision Point (PDP) that evaluates access control requests against policy rules. The evaluation is done by resolving all the rules in the policy. 
Current access control architectures separate between the PEP implementation and the PDP mainly for two reasons:
\begin{itemize}
\item Specifying the policy independently from the application enables to save time, cost and effort during the maintenance phase. 
Recall that access control policies updates are frequent due to the dynamic behavior of assets, resources and security mechanisms that regulate systems.
\end{itemize}
Access control policies can be specified by many languages. In what follows, we consider XACML polices written in XACML language.

%%%% Figure here
\subsection{XACML Policies}
This section describe background of XACML policies, policy models, and model checking.
\begin{figure}[t]%{t}
%\begin{figure}[firstnumber=100]
\begin{CodeOut}
\begin{alltt}
 1 <Policy PolicyId="\textbf{Library Policy}" RuleCombAlgId="\textbf{Permit-overrides}">
 2  <Target/>
 3    <Rule RuleId="\textbf{1}" Effect="\textbf{Permit}">
 4      <Target>
 5        <Subjects><Subject> \textbf{BORROWER} </Subject></Subjects>
 6        <Resources><Resource> \textbf{BOOK} </Resource></Resources>
 7        <Actions><Action> \textbf{BORROWERACTIVITY} </Action></Actions>
 8      </Target>
 9	    <Condition>
10        <AttributeValue> \textbf{WORKINGDAYS} </AttributeValue>
11      </Condition>
12    </Rule>
13    <Rule RuleId="\textbf{2}" Effect="\textbf{Deny}">
14      <Target>
15        <Subjects><Subject> \textbf{BORROWER} </Subject></Subjects>
16        <Resources><Resource> \textbf{BOOK} </Resource></Resources>
17        <Actions><Action> \textbf{BORROWERACTIVITY} </Action></Actions>
18      </Target>
19	    <Condition>
20        <AttributeValue> \textbf{HOLIDAYS} </AttributeValue>
21      </Condition>
22    </Rule>
23    <Rule RuleId="\textbf{3}" Effect="\textbf{Permit}">
24      <Target>
25        <Subjects><Subject> \textbf{SECRETARY} </Subject></Subjects>
26        <Resources><Resource> \textbf{BOOK} </Resource></Resources>
27        <Actions><Action> \textbf{FIXBOOK} </Action></Actions>
28      </Target>
29	    <Condition>
30        <AttributeValue> \textbf{MAINTENANCEDAY} </AttributeValue>
31      </Condition>
32    </Rule>
33      <!-- A final, "fall-through" rule that always Denies -->
34    <Rule RuleId="\textbf{FinalRule}" Effect="\textbf{Deny}"/>
35 </policy>
\end{alltt}
\end{CodeOut}

\vspace*{-3.0ex} \caption{An example policy specified in XACML}
 \label{fig:example}
\end{figure}
XACML (eXtensible Access Control Markup
Language)~\cite{oasis05:xacml} is a language specification standard
%designed by OASIS.
published by Organization for the Advancement of Structured
Information Standards (OASIS).
An XACML access control specification consists of a policy set and a
policy combining algorithm.
XACML supports for various policy models such as Role Based Access Control (RBAC)~\cite{anderson04:rbacxacml,ferraiolo01:proposed} and organization-based access control (OrBAC)~\cite{kalam03:orBac}. For RBAC and OrBAC, various job functions are associated to roles (e.g., staff or employee) that a user possesses. Permissions or denials to take an action on certain objects are assigned to specific roles (instead of users). OrBAC supports for 
extra features such as role, activity (i.e., action), and view (i.e., object) hierarchy. Figure~\ref{fig:example} is an OrBAC policy example since this example expresses roles such as ``Secretary'' and ``Borrower'' are associated with subject attributes and policy decisions are made through specific roles.
Let $Conditions$ be the set of the environmental context
such as working days or holidays, a file size, and a user's task authorization level. 
Let $S$, $O$, $A$, and $C$ denote all the subjects,
objects, actions, and  $Conditions$, respectively, in an access control system.
An XACML policy consists of a \Intro{policy set}, which consists
of \Intro{policy sets} and \Intro{policies}. A \Intro{policy} consists
of a sequence of \Intro{rules}, each of which
specifies under what conditions $C$ subject $S$ is allowed or denied
to perform action $A$ (e.g., read) on certain object (i.e., resources) $O$ in a system.

A rule $R$ is of the following form:
\begin{center}
$R$ $\subseteq$ $S$ $\times$ $A$ $\times$ $O$ $\times$ $C$ $\longrightarrow$ $Dec$
\end{center}
where $Dec$ denotes a decision, which is either permit or deny.
A user's request is evaluated against a policy.
A request matches with a rule if the request satisfies the rule's
attributes. Then the rule's decision can be returned.

For R1 = 
Formally, a request $Q$ in the following form matches $R$:
\begin{center}
$Q$ $\subseteq$ $S_q$ $\times$ $A_q$ $\times$ $O_q$ $\times$ $C_q$ where $S_q$ $\subseteq$ $S$, $A_q$ $\subseteq$ $A$, $O_q$ $\subseteq$ $O$, and $C_q$ $\subseteq$ $C$.
\end{center}


More than one rule in a policy may be applicable to a given request.
The \Intro{rule combining algorithm} is used to combine multiple
rule decisions into a single decision. There are four standard rule
combining algorithms: \CodeIn{deny-overrides}, \CodeIn{permit-overrides}, \CodeIn{first
applicable}, and \CodeIn{only-one-applicable}. The
\Intro{deny-overrides algorithm} returns \CodeIn{Deny} if any rule
evaluation returns \CodeIn{Deny} or no rule is applicable. The
\Intro{permit-overrides algorithm} returns \CodeIn{Permit} if any
rule evaluation returns \CodeIn{Permit}. Otherwise, the algorithm
returns \CodeIn{Deny}.
The \Intro{first-applicable algorithm} returns whatever the
evaluation of the first applicable rule returns. The
\Intro{only-one-applicable} algorithm returns the decision of the only
applicable rule if there is only one applicable rule, and returns
error otherwise.

Figure~\ref{fig:example} shows an example policy specified
in XACML. The example policy consists of three XACML rules used in our real-life library access
control policy subject, called $LSM$~\cite{mouelhi09:tranforming}.
Note that we simplified XML formats to reduce
space for this example.
Lines 3-12 describe a rule that \CodeIn{borrower} is Permitted for \CodeIn{book} \CodeIn{borroweractivity} (e.g., borrowing books) in \CodeIn{working days}.
Lines 13-22 describe
a rule that \CodeIn{borrower} is Denied for \CodeIn{book} \CodeIn{borroweractivity} in \CodeIn{holidays}.
Lines 23-32 describe
a rule that \CodeIn{secretary} is Permitted for \CodeIn{book} \CodeIn{fixing} in \CodeIn{maintenance day}.
As these rules are combined using the permit-overrides
algorithm, the \Intro{permit-overrides algorithm} returns the
\CodeIn{Permit} if a request matches at least one of
rules with permit decisions. For example, if rules 2 and 3 are applicable to a request, the decision
evaluated from rule 3 is given higher priority than that of rule 2.


\subsection{Regression Testing}
Software testing \cite{Myers:1979:AST:539883} refers to the activity of generating Tests Cases to verify the conformity of ouput results provided by a program to its expected 
output with respect to its functional and non functional requirements. With the increasing complexity of software systems, this activity is becoming more and more challenging as it 
should provide a certain trade-off between budget, time and quality.

The software is a subject to many changes that can occur at the design phase or at the maintenance level to comply to changes in requirements.
this implicates the necessity of retesting the system to verify that the subsequent changes have not introduced some errors on the sytem or altered its functioning.

Softawre products are subject to changes that occur at the design stage or in later stage at the deployment or maintenance phases. These changes are intended to meet changes
 in the requirements or to overcome errors that can be detected in later stages of software life cycle. This implies retesting the system to verify that new changes have not altered 
initial system behavior. Regression testing denotes this research area. As stated by \cite{Rothermel:1996:ART:235681.235682}:
``Given a program P, a modified version P', and a set T of test cases used previously to test P, regression analysis and testing techniques attempt
to make use of a subset of T to gain sufficient confidence in the correctness of P' with respect to behaviors from P retained in P'.`''

The main objective of this research field is to minmize the costs from rerunning the initial test cases that have been performed before the deployment of the software product, while 
maintaining a high capability for the selected tests to detect potential errors that are induced by changes.


\subsubsection{Regression testing: Selection and Augmentation}
There is two aspects that should be considered conjointly in Regression techniques: (1) The first aspect is the regression test selection problem which aims at minimizing 
the percentage of test cases that has to be chosen from the overall test suite or reduce the costs from rerunning all system tests.
The regression test selection technique is called safe when it enables to detect 100\% of the faults.
(2) The second aspect called augmentation technique aims at adding new tests to cover the new parts resulting from changes.

\subsubsection{Regression testing in the context of software of policy based systems}
It is important to test policy based software systems to verify that new rules have not introduced bad changes on access control mechanisms that reside already in the system.
In \cite{mouelhi09:tranforming}, we have applied mutation testing on access control policies.
\\
TO DO Describe the work DONE SO FAR...





